---
output: github_document
---

# "USGS Gage Landcover change"
<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include=FALSE, message = F, warning = F}
library(dplyr)
library(sf)
library(ggplot2)
knitr::opts_chunk$set(echo = TRUE,
                      eval = TRUE,
                      warning = FALSE)
```

## Process

For all GAGES-II basins in CONUS (n = ~9,000), identify the change in Anderson Level 1 land cover classes between 2001 and 2019 using the NLCD.

## Data Directory: 

  - parquet file of basins
  
```{r}
basins = sfarrow::st_read_parquet('data/usgs-lc-basins.parquet') 
ref = basins %>% 
  sf::st_centroid() %>% 
  select(GAGE_ID)
```
  
  - Meta data about all USGS stations was aggregated and stored in CSV files.

```{r, eval = FALSE}
file = list.files("./data/", pattern = "sites_", full.names = TRUE)
meta = bind_rows(lapply(file, read.csv)) %>% 
   mutate(GAGE_ID = sprintf("%08s", GAGE_ID), X = NULL)
```

  - Outputs were chunked as well and saved as a series of CSV files.
  
```{r}
file = list.files("./data/", pattern = "output_", full.names = TRUE)

results =  bind_rows(lapply(file, read.csv)) %>% 
     mutate(GAGE_ID = sprintf("%08s", GAGE_ID), X = NULL) %>% 
  right_join(ref) %>% 
  st_as_sf() %>% 
  na.omit() %>% 
  group_by(description) %>% 
  mutate(scaled = scale(perD)) %>% 
  arrange(abs(scaled)) %>% 
  ungroup()

ggplot() + 
  geom_sf(data = results, aes(color = scaled, size = abs(scaled)), 
          shape = 16) +
  scale_color_gradient2(low = "red", 
                        high = "blue", 
                        na.value = "transparent") + 
  facet_wrap(~description) + 
  scale_size(range = c(0, 3), guide = 'none') +
  theme_dark()
```

## Search Basins by Category Example

```{r}
results %>% 
  filter(description == 'forest') %>% 
  slice_max(perD, n = 10) %>% 
  st_drop_geometry()
```
  
# Working with this data:

```{r}
paint::paint(read.csv("output/results.csv"))

```